Naming Conventions for GRSSLCM

### 2020-07-17 99-admin/naming-conventions/names.Rmd
Edit naming-convention rmd root directory
This is for consistency with the rules - all paths should be relative to the project root

Also add in some more comments and context

```{r setup, include = F}
knitr::opts_chunk$set(echo = F)

# load packages
library(knitr)
library(kableExtra)
```

@@

```{r read-manip-table}
# raw input file
tab = read.csv("names.csv", allowEscapes = T, stringsAsFactors = F)

@@

colnames(tab) = c("", "In Code", "Symbol", "Description", "Notes")
```

```{r create-table-fun}
create_table = function(group) {
  kable(tab[tab[,1] == group,-1], format = "html", escape = F, row.names = F) %>%
    kable_styling(full_width = F, bootstrap_options = c("condensed", "striped"))
}
```

@@

>>>>

```{r directories, include = F}
# set root directory to the project directory: two levels up from this location
knitr::opts_knit$set(root.dir = "../../")
```

```{r pkg-and-options, include = F}
# load packages
source("00-packages.R")

# set global knitting options
opts_chunk$set(echo = F)
```

@@

```{r read-manip-table}
# raw input file
tab = read.csv("99-admin/naming-conventions/names.csv", allowEscapes = T, stringsAsFactors = F)

@@

# edit column names
colnames(tab) = c("", "In Code", "Symbol", "Description", "Notes")
```

```{r create-table-fun}
# function to create a table based on the type of quantity
create_table = function(group) {
  kable(tab[tab[,1] == group,-1], format = "html", escape = F, row.names = F) %>%
    kable_styling(full_width = F, bootstrap_options = c("condensed", "striped"))
}
```

@@

_NOTE_: The "code" column specifies how the variables/parameters will be referred to in the JAGS model code and post-processing code, not necessarily the same as the raw data or preparation of raw data code.
